\section*{Retrospective meeting}
\subsection*{Participants}

\textbf{Convener}:\scrummaster{} \\
\textbf{Facilitator}: \facilitator{}  \\
\textbf{Recorder}: \scrummaster{} \\
\textbf{Others}: \groupleader{} \\
\textbf{Absent}: 

\subsection*{Agenda}
\begin{itemize}
    \item What went well?
    \item What could have been done better?
    \item Is there something new that the team wants to start doing?
    \item Is there something that puzzles us?
\end{itemize}

\subsection*{Retrospective}

\noindent

\par

\begin{Parallel}[v]{0.48\textwidth}{0.48\textwidth}
\ParallelLText{\noindent

\textbf{What did we do well?}
\begin{itemize}[rightmargin=.52\textwidth]
    \item{The stories were divided into multiple small tasks, which made development very efficient.}
    \item{The group improved with holding 8 hours limit for work day.}
    \item{Code quality became better, as we learned JavaScript and did not care about backwards compatibility beyond WebAssembly.}
    
\end{itemize}
}
\ParallelRText{\noindent

\textbf{What should we have done better?} 
\begin{itemize}[rightmargin=.52\textwidth]
    \item{We should have worked more efficiently with the front-end refactoring.}
    \item{The slow refactoring made it hard to complete other tasks.}
    \item{The refactoring covered a lot of files and made for a difficult merge.}
\end{itemize}

}
\ParallelPar
\end{Parallel}

\subsection*{Is there something new that the team wants to start doing?}
We will focus heavier on setting up sub-tasks as smaller tasks proved use-full in previous sprint.

\subsection*{ Is there something that puzzles us?}
We should look more into user-studies, as we had not considered the ethics board required for formal user-studies.

\newpage
