\section*{Retrospective meeting}
\subsection*{Participants}

\textbf{Convener}:\scrummaster{} \\
\textbf{Facilitator}: \facilitator{}  \\
\textbf{Recorder}: \scrummaster{} \\
\textbf{Others}: \groupleader{} \\
\textbf{Absent}: 

\subsection*{Agenda}
\begin{itemize}
    \item What went well?
    \item What could have been done better?
    \item Is there something new that the team wants to start doing?
    \item Is there something that puzzles us?
\end{itemize}

\subsection*{Retrospective}

\noindent

\par

\begin{Parallel}[v]{0.48\textwidth}{0.48\textwidth}
\ParallelLText{\noindent

\textbf{What did we do well?}
\begin{itemize}[rightmargin=.52\textwidth]
    \item{The pair programming worked very well for parsing function calls task.}
    \item{The team managed to complete two complicated problems that had lasted for several sprints.}
    \item{The pair programming helped getting all members up to date with the different component.}
    
\end{itemize}
}
\ParallelRText{\noindent

\textbf{What should we have done better?} 
\begin{itemize}[rightmargin=.52\textwidth]
    \item{The pair programming went slowly when some group members were tired.}
    \item{The team should have followed the time stated in project plan a lot better.}
\end{itemize}

}
\ParallelPar
\end{Parallel}

\subsection*{Is there something new that the team wants to start doing?}
The team will be more open to pair programming and will let tired members work on their own tasks. 

\subsection*{ Is there something that puzzles us?}
We are still uncertain of how long the visualization of function calls will take. 

\newpage
