\section*{Retrospective meeting}
\subsection*{Participants}

\textbf{Convener}:\scrummaster{} \\
\textbf{Facilitator}: \facilitator{}  \\
\textbf{Recorder}: \scrummaster{} \\
\textbf{Others}: \groupleader{} \\
\textbf{Absent}: 

\subsection*{Agenda}
\begin{itemize}
    \item What went well?
    \item What could have been done better?
    \item Is there something new that the team wants to start doing?
    \item Is there something that puzzles us?
\end{itemize}

\subsection*{Retrospective}

\noindent

\par

\begin{Parallel}[v]{0.48\textwidth}{0.48\textwidth}
\ParallelLText{\noindent

\textbf{What did we do well?}
\begin{itemize}[rightmargin=.52\textwidth]
    \item{The team managed to finish most of testing related issues.}
    \item{The tasks were divided well enough that unexpected hinders allow members to just change over to a different task until problems were resolved.}
    \item{The team realized that the complexity of previously written code was higher than expected.}
    
\end{itemize}
}
\ParallelRText{\noindent

\textbf{What should we have done better?} 
\begin{itemize}[rightmargin=.52\textwidth]
    \item{The team took longer than expected to setup testing environment}
    \item{Large portions of the previously written code did not lend itself to creating simple tests.}
\end{itemize}

}
\ParallelPar
\end{Parallel}

\subsection*{Is there something new that the team wants to start doing?}
The next sprint will focus on more complicated tasks so the team will hold pair programming sessions for increased productivity. Team has planned to spend about 8 hours per day on pair programming session til the issues are resolved and spend the rest of the time working on the testing related tasks individually if possible.

\subsection*{ Is there something that puzzles us?}
We are still worried about estimating the three most complicated tasks. We have tried to estimated them before and been significantly off. We hope the pair programming will help.

\newpage
