\section*{Retrospective meeting}
\subsection*{Participants}

\textbf{Convener}:\scrummaster{} \\
\textbf{Facilitator}: \facilitator{}  \\
\textbf{Recorder}: \scrummaster{} \\
\textbf{Others}: \groupleader{} \\
\textbf{Absent}: 

\subsection*{Agenda}
\begin{itemize}
    \item What went well?
    \item What could have been done better?
    \item Is there something new that the team wants to start doing?
    \item Is there something that puzzles us?
\end{itemize}

\subsection*{Retrospective}

\noindent

\par

\begin{Parallel}[v]{0.48\textwidth}{0.48\textwidth}
\ParallelLText{\noindent

\textbf{What did we do well?}
\begin{itemize}[rightmargin=.52\textwidth]
\item{The group worked well and was able to make of for much of the time lost in the last sprint.}
\item{The group was able to integrate GUI framework ahead of schedule.}
\item{Backend was refactored to a stage where it could be used for the sprint.}
\item{The team learnt about antlr quicker than anticipated.}
\end{itemize}
}
\ParallelRText{\noindent

\textbf{What should we have done better?} 
\begin{itemize}[rightmargin=.52\textwidth]
  \item{The group was forced to work overtime to the point of exhaustion.}
  \item{Could not immediately find a good force directed graph library/algorithm that would take the input data we required.}
  \item{There was very little time to document code or creating tests.}
  \item{The group realized late that their parser implementation was not sufficient.}
  \item{The estimations of time reacquired per task was significantly off.}
  \item{The tasks conflicted forcing members to do pair programming on relatively simple programming components.}
\end{itemize}

}
\ParallelPar
\end{Parallel}

\subsection*{Is there something new that the team wants to start doing?}
The team will divide the stories further so that each member can be expected to finish several by the end of the sprint and prevent working in the same part of the code base. The tasks should also be clarified better and be more concise.

\subsection*{ Is there something that puzzles us?}
We need to look into Antlr visitor versus Antlr listeners. 
We should look into professional frontend and file structure as well as programming patterns.
We might have problems with latency and computational complexity.
\newpage
