\section*{Meeting with Product owner And supervisor}
\subsection*{Participants}
\textbf{Convener}: \productowner{}\\
\textbf{Facilitator}: \facilitator{}  \\
\textbf{Recorder}: \scrummaster{}  \\
\textbf{Others}: \groupleader{} \\
\textbf{Absent}: 

\subsection*{Agenda}
\begin{itemize}s
    \item Feedback
\end{itemize}

\subsection*{Minutes}
Life is good, yet bachelor is going slowly. We have used the week for testing. It goes slower than expected partially because we are using multiple systems with multiple testing environments, (AVA .js, go test .go and j-unit .java). We have some problems with j-unit as its difficult to mock with antlr. We have found a few bugs as a result of testing, like URI validation and unnecessary Fatal instead of error call. 
We have productively 2 weeks of development left which can cause a problem for the amount of work left. 
We want to Finnish scoping on front end, function calls, class parsing and cyclomatic complexity. Would be nice with cashing as well and  possibility of only saving last "x" repose.

We should structure the report to show the testing as a quality assurance and note that everything before the point of test-writing is likely to work.

Both supervisor should probably be on the list, but it should be noted when Christopher became supervisor.

About unfinished quality metrics (connacense), we could mention the possible with definition in the background and mention them later and in the future work having a red thread through it. 
\newpage