\section*{Meeting with Product owner}

\subsection*{Participants}
\textbf{Convener}: \productowner{}\\
\textbf{Facilitator}: \facilitator{}  \\
\textbf{Recorder}: \scrummaster{}  \\
\textbf{Others}: \groupleader{} \\
\textbf{Absent}: 

\subsection*{Agenda}
\begin{itemize}
    \item Specific constraints to include.
    \item Open stack for deployment.
    \item MIT License.
    \item Interactions.
    \item Expected systems effect. 
    \item Worries.
    \item other.
\end{itemize}

\subsection*{Minutes}

\subsubsection*{Specific constraints to include}

Should check out juristical constraints yourself.
should work with gitrepo but would also be nice for it to work on zip files.

\subsubsection*{Open stack for deployment}
Would not like OpenStack as a dependencies, docker would be nice. would be nice to be able to run it on "My machine". 

\subsubsection*{MIT License}

Perfect.

\subsubsection*{Interactions}

Open collapse like makes sense in 2D is most important other ideas are also good. Must always be able backtrack.

For the gathering of related datastructures we should check out force directed algorithms.
\subsubsection*{Expected systems effect}

Should be able to be used in a classroom setting where all students use the system at a time.

\subsubsection*{Worries}

You should not focus on worry, just try to learn as much as possible.

\subsubsection*{Other}

For the quality metrics we should check out cyclomatic complexity and connascence metrics. \\
We should also check out profiling and software quality tools as used by other IDEs like visual studio. 
\\
\\
Kotlin would be nice for mobile programming. \\
Would be nice to have an exposed POSIX API for accessing data without visualizations and be able to choose what information these requests should contain, in the sense of static analysis data, quality metrics data and/or connectivity data.

\newpage