\section*{Meeting with Supervisor}

\subsection*{Participants}

\textbf{Convener}: \supervisor{}\\
\textbf{Facilitator}: \facilitator{}  \\
\textbf{Recorder}: \scrummaster{}  \\
\textbf{Others}: \groupleader{}                         \\
\textbf{Absent}: 

\subsection*{Agenda}
\begin{itemize}
    \item Feedback on report draft

\end{itemize}

\subsection*{Minutes}

\subsubsection*{Feedback on the report}
The introduction should be more general, making it more specific later on. Changing it from "Finding libraries or frameworks" to "analyzing source code". 
There is too much use of the word "Should". The report is meant to be binding and contain what must be done. If additional should be added, then that should be clearly separated.

% fixed
There is a grammatical error in 2.3.1. 


In 3.1, when talking about the development process, it gets a bit too loose. You should add where in this section your project acts. Don't just add this in "bounds".

When you mention that the system can be useful for documenting, this conflicts with the usecase being for identifying good libraries and framework.

It's a bit confusing when you use the words "Data structure" and "function" interchangeably. 

In terms of risk analysis, you have set that one or more members of group are unavailable for a long period of time as priority 7, but have not set up a mitigation for this. 
Add priority column on "mitigation table". 

Version Lava lizard and version 1.0, before "all development should be done in the middle of April"; It's ok to have time to write on the report. But the quantity you have added is more than usual. Usually one only allocates 2-4 weeks.

Your user studies have been set up with a lot of other stuff. It would be better if it was mentioned how much time is used on that part, as now it looks like there is not enough time.

This is a complex thesis, It is important to do user study in correct manners. User studies is a hard process and we as developers do not have much experience in this topic. Usually the user studies requires 5 - 20 users and more than a week to be properly planned and conduct.

It seems strange that we will be doing all analysis ourselves. Could look into "Sonar qube" for a part of analysis.

It would be better if its added that you will find software to do part of the features for us.

Supervisor will find out the delivery data of bachelor thesis.

Supervisor does not know any automatic usability and accessibility tool.

\newpage