\chapter{Implementation}
\label{chap:implementation}
%This has the description of how you actually went about implementing the project.  This should be focused on the interesting challenges and how those related to the project.

\section{Front-end web development}
\subsection{Overall design implementation}
\label{subsection:frontendOverallDesignImplementation}
%Explain the module pattern
\input{inc/figures/codesnippets/modulepattern.tex}


% Team background oop.
The team has a background in \gls{oop} and very limited experience with JavaScript. Implementation of \gls{frontend} started off as simple functionalities but become a problem as the team progressed. \Gls{frontend} was responsible for many things such as \gls{fdg}, graphics, \gls{gui} and etc. It became a problem that the code was expanding and the team did not know how to control files size but also how to properly divide the code sections in different files.
During refactoring the team had done research and found different design pattern where module pattern \cite{scotch:javascriptpatterns} was very similar to classes. "Class" was also found but though research is seemed the module pattern was very commonly used. One reason to choose module pattern was that the team wanted \gls{frontend} to be object-oriented, so that only the object would know about its properties and functionalities. Another reason to do so, is that it makes code easily understandable by use of getters and setters, as shown in the figure \ref{lst:module}.
The team then decided to implement module pattern to structure front-end. 

There were two libraries used in \gls{frontend}; THREE.js and ImGUI-js. Three.js is a recommended \cite{cmarix:threejs} 3D graphics library based on WebGL. It also contains many different functionalities such as scenes, meshes, camera, lights, etc. This fits the requirements and worked for this purpose. Dear ImGUI is a windowing library for C++ that all team members were familier with form the graphics programming course \cite{course:graphics}. Dear ImGUI has a binding to JavaScript called ImGUI-js that uses TypeScript and Emscripten. This way the team was able to integrate ImGUI-js into the system. The library is easy to use and fits the teams purpose.

\subsection{Force-directed graph}
The \gls{fdg} object maintains a tree of nodes and manages the inter-dependencies between the nodes in the tree. It references the tree through its root, which in turn references its children. The main force calculations and scope handling are done in the nodes, so the \gls{fdg} functions as a wrapper.

\subsubsection{Position calculation}

\newglossaryentry{hookesLaw}{name={Hooke's law}, description={Describes a relationship between spring compression and force applied \cite{hooke1678}}}
\newglossaryentry{logit}{name={logit}, description={Inverse of the Sigmoid function \cite{wordpress:logitandsigmoid}}}
\newglossaryentry{sigmoid}{name={sigmoid}, description={Used to transform values on $(-\infty, \infty)$ into numbers on $(0, 1)$ \cite{wordpress:logitandsigmoid}}}

%Explain Logit and force. Could probably add graph from ProfProg rapport.
\input{inc/figures/codesnippets/forceCalculation.tex}
To calculate the position, \gls{fdg} consider the root as the projects global scope, then extracts its children and calculates the force between them. Each child is itself a scope within its parent. The force within each scope is calculated separately to assure that the structure stays within its scope. Listing \ref{lst:getTotalForce} shows that the force calculation depends on whether or not there is a link between the nodes. If there is a link, it is considered a positive attraction, otherwise it is considered a repulsion. 

The idea behind the attractive force calculation is to function like a spring; the more energy is required the further apart they are. \gls{hookesLaw} was considered for the calculation. The implemented calculation uses $ \log_{10} $ on the distance between each node divided by the minimum distance and size of each data structure. This is to create a repulsion when the two structures are too close and a strong attraction when they are too far apart. 

The repulsion uses the Inverse-square law \cite{enc:inverseSquare} to grow weaker over a distance.

\input{inc/figures/gravityPlot.tex}
The figure also show the gravity force calculation. Gravity attracts all structures towards the center of their scope. The center is the zero vector and updated with parents position when added to the scene graph after all relative positions have been calculated. The gravity calculation is based on \gls{logit}, as this implementation gives a gravity force approaching infinity when distance between structures approach max distance. This infinite force prevents structures from escaping their parent scope. The problem of limiting the position within a scope seemed related to \gls{sigmoid} that the group had experience with through REA1121 - Mathematics for Programming \cite{course:progMath}. \Gls{sigmoid} seemed relevant as it allowed for manipulation of its range and gave a smooth curve. Problem with \gls{sigmoid} is that if $x$ is distance and $y$ is force, then it would clamp on force rather than distance. \gls{logit} was described as the inverse of \gls{sigmoid} and would therefore clamp on distance, limiting the structure within its scope. As the distance between center and a structure can not be negative and gravity should never be negative, \gls{logit} was altered so it crossed the x axis at origin and approached infinity when it approached max distance like shown in figur \ref{fig:gravityPlot}.

\subsubsection{Recursivity of node}
\label{subsubsec:recuriviryOfNode}
%Explain the use of local/global index.
\input{inc/figures/treeIndex.tex}
\input{inc/figures/codesnippets/nodeRecursion.tex}
The \gls{fdg} tree requiers each node to have an identifier so that they can identify each other for linking and potentially other purposes. This identifier is based on position in the tree and for easy searching. The identifier acts as an index in an array, starting at 0 and increasing with one for each node. When it was implemented, it had to be created based only on information of its sub-tree. This meant its global index in the tree could not be calculated, only its local index where the node is the root of it's sub-tree. Once the tree is set in the \gls{fdg}, all nodes are given their global index. Before the global index is given, it can be calculated from the root node by using the local index given while building the tree. The local index is one greater than the sum of each child's local index. Figure \ref{fig:treeIndex} shows the relationship between local and global index while listing \ref{lst:getNode} shows a recurcive call to find a node with global index using the local index. LocalOffset in listing \ref{lst:getNode} refers to the offset from global index to local index caused by the parent node having a subtree to the left of the node being checked. Figure \ref{fig:treeIndex} is simplified by counting from  one instead of zero. The actual global index starts at zero to fit with array index. To account for the local index going from one and global index being accessed from zero, figure \ref{lst:getNode} shows index and local-index being subtracted by one in the conditionals.

\subsection{Localization}
\newglossaryentry{localization}{name={localization}, description={Translating a product into different languages or adapting a product to a country or region}}

\input{inc/figures/codesnippets/locale.tex}

The current implementation of \gls{localization} is not very good due to the way sentences are stored. The reason for this implementation is that it was quick, easy to setup and easy to use. Also the team did not want to spend much time on this feature as it was not a requirement, but would allow for scalability in the future. There might be better ways of doing this, for instance the Mobile Programming course\cite{course:mobileWearable} covers the use of Android framework that uses separate files for each locale. 

In the current system, sentences are stored as objects within a list, where each sentence has a list of the different languages and the sentence itself in that language. To find a sentence, one first have to find the correct sentence based on the identifier and then find the correct language based on the currently selected language. As more sentences are localized, the time taken to find the latter sentences is increased due to the number of sentences to search through. A better way of implementing this would be to sort primarily on the languages them selves in a \gls{keyvaluemap}, where key is the language and value is a list of sentences. This would eliminate the use of list for languages and making the search process more effective. To optimize even further, the sentence list inside the \gls{keyvaluemap} could also be made into a \gls{keyvaluemap} for the same reason. 

"getSentence" is the function responsible for fetching sentences in the currently selected language. If the sentence could not be found it defaults to the English language. 

\subsection{Graphics}
\label{subsection:graphicsFunctionLinking}
\newglossaryentry{scenegraph}{name={scene graph}, description={A collection of nodes in a graph or tree structure which arranges the logical and often spatial representation of a graphical scene \cite{dollner2000generalizedSceneGraph}}}

\input{inc/figures/codesnippets/functionLinking.tex}

% The sequence of the paragraphs has to be looked at

% Introduce THREE.js?

% Scene graph
\href{https://threejs.org/}{THREE.js} uses a scene structure called \gls{scenegraph}. The structure in the \gls{scenegraph} allows to put object in a hierarchy and if the parent moves in the world, the children follow to retain their position in relation to their parent. 

% Difficulties in linking
The \gls{scenegraph} caused a lot of confusion in linking the different functions based on calls, as the functions were set to a relative position whilst the calls were set using absolute position. The solution for this was to use the \href{https://threejs.org/docs/#api/en/core/Object3D.updateMatrixWorld}{updateMatrixWorld} function from \href{https://threejs.org/}{THREE.js}'s \href{https://threejs.org/docs/#api/en/core/Object3D}{Object3D} which is the base class of \href{https://threejs.org/docs/#api/en/scenes/Scene}{Scene}. It runs a full update on itself and all its successors within the \gls{scenegraph} and updates their world positions. After this, it's possible to use \href{https://threejs.org/docs/#api/en/math/Vector3.setFromMatrixPosition}{setFromMatrixPosition} function from \href{https://threejs.org/}{THREE.js}, which uses the world matrix to calculate the actual position from world origin. 

Drawing of objects in \href{https://threejs.org/}{THREE.js} can be done by using the \href{https://threejs.org/docs/#api/en/objects/Mesh}{Mesh} object. This object takes a \href{https://threejs.org/docs/#api/en/core/Geometry}{Geometry} which is the shape made from vertices, and a \href{https://threejs.org/docs/#api/en/materials/Material}{Material} which gives the object characteristics and functionalities, e.g. Phong shading \cite{acm:phongShading1986article}, shadow mapping \cite{acm:perspectiveShadowMap2002article} capabilities, opacity, etc. These can then be added to the scene and updated if needed. 

The generation of the links is performed by looping over each nodes links and fetching the respective node's world position. These positions are given to a \href{https://threejs.org/}{THREE.js} \href{https://threejs.org/docs/#api/en/core/Geometry}{Geometry} and combined with a \href{https://threejs.org/docs/#api/en/materials/LineBasicMaterial}{LineBasicMaterial} object, which results in a line between the two positions. % Last sentence is probably unecessary

% Shapes
Within the visualization there are a bunch of shapes. Each shape represents some kind of data structure, e.g. class, function, etc. Instead of building custom shapes, it was decided to use \href{https://threejs.org/}{THREE.js} built-in geometries. 

% Mention use of STYLE for color-scheme
The style feature is implemented in the same way as the localization. It contains a \gls{json} data structure which has a list of color schemes and shape settings. The JavaScript Module pattern was used so the configuration data structure could be encapsulated to maintain a good structure and keep the application as object oriented as possible. 

% More of a discussion section?
The group wanted the appearance of the application to be customizable to the different vendors, if they have a certain color scheme or style they follow or high contrast styles which highlights different aspects of the program better for those with visual disabilities. To help people that are colorblind it was decided to use different shapes for the separate data structures and a high contrast as well as colorblindness-specific color schemes. These color schemes are not currently implemented, but they will be if any work is continued. The only color schemes added are a SublimeText-inspired scheme and a default color scheme.

% Camera and lighting

\subsection{Interaction}
\input{inc/figures/codesnippets/onClick.tex}
\newglossaryentry{keyvaluemap}{name={key-value map}, description={A data structure that maps keys to values}}
\newacronym{dom}{DOM}{Document Object Model}
The interaction that exists in the system is interaction with function representations and windows. The text within the window showing data structure implementation, won't wrap but will be hidden and can be seen by temporarily expending the window through clicking and dragging on the lower right corner of the window. Once released the window will reset to its original layout so that it does not hide the visualization.

The interaction with data structures is done using a technique called \gls{raycast}. \Gls{raycast} is built into \href{https://threejs.org/}{THREE.js} which is used for mouse picking objects from a 3D space. The function onMouseClick is added as an event listener to JavaScript built in window, which represents window containing \gls{dom}.

As the listing \ref{lst:onClick} shows, first the mouse position is normalized based on screen coordinates, then the raycaster is attached to the camera and normalized mouse coordinates are given so that the ray is cast from the camera to the mouse position, once the user clicks in the scene. The \gls{raycast} returns a list of intersected objects. This list is sorted in the order that objects were intersected by the ray. This way the first element of the list will always be object that user wants to interact with.

The interacted object gives its name that was assigned before it was added to the scene. A \gls{keyvaluemap} of function models is created, whilst the project \gls{json} is being parsed in \gls{frontend}. This \gls{keyvaluemap} contains all metadata about all functions that are visualized and is used to identify the actual model the user has clicked. Once the actual function model is found, it can be used to fetch the models implementation and visualize it in the implementation window. 

\section{Back-end}

\subsection{Overall design implementation}
\newacronym{url}{URL}{Uniform Resource Locator}
\input{inc/figures/codesnippets/apiRouting.tex}
The \gls{backend} is divided into two parts as mentioned in the Technical Design chapter; Go \gls{api} and \gls{jap}.

As the listing \ref{lst:apiRouting} shows, some of the entry points has the repository ID as part of their \gls{url}. This \gls{url} path variable is sent from \gls{frontend} and is used to identify a repository from the database. The placeholder for repository ID is implemented using Gorilla Mux. The idea behind doing this was that the entry point would show what repository the \gls{api} should deal with and what operation should be done on it based on the \gls{url}.

The ".../initial/" is the main request that uses \gls{websocket} and communicates with \gls{jap} by giving it a project file at a time, and expects a \gls{json} with parsed code in return. Whilst being parsed the \gls{frontend} will recieve a message about the file being processed through "message" channel of \gls{websocket} for server feedback to user. In Go \gls{api}, parsed code \gls{json} is added into the project model. Once all project files are parsed the project model is converted into \gls{json} and sent as a response with the "close" channel of \gls{websocket}. 

Initially the plan was to use \gls{antlr} in Go for parsing as \gls{antlr} has a target for Go. Whilst the team was trying to integrate \gls{antlr} into Go, it came into focus that the grammar files that the team was planning to use had embedded Java code, which would not have worked in Go. Therefore Java seemed to be natural choice to fallback to for parsing and since \gls{antlr} was natively made in Java. The team also had some experience in Java through Mobile/Wearable programming course \cite{course:mobileWearable}. The package "os/exec" in Go was be used to execute \gls{jap} and receive its output.

There are two libraries used in the \gls{backend}: Gorilla mux and JSONObject.

Gorilla mux is a library that is widely used for \gls{url} routing for Go projects. This library was mentioned in the Cloud Technology course \cite{course:cloud}, so the team already had an understanding of it and made it very easy to integrate. 

In \gls{jap} the JSONObject library was used to construct \gls{json} for each data structure model. Once every line of code has been parsed, the file model which contains many different properties such as namespaces, functions, variables, will loop over each property to store as \gls{json}.
 
% endpoints

% gorilla mux as a librarary
% json in java


\subsection{Processing server in Go}    \label{subsection:Go}

\subsubsection{REST and WebSocket}
\input{inc/figures/codesnippets/websocketSuccessMessage.tex}
Initially the requirements asked for a \gls{rest} service, but this was loosened in favor of \gls{websocket} to allow for updating the user on progress of lengthy tasks. As \gls{http} responses has more extensive status information than \gls{websocket}, the team decided to use the responses as a wrapper for a trimmed down \gls{http} response with \gls{http}Status code, \gls{http}Status text and body containing the requested information. Listing \ref{lst:websocketMessageSuccess} shows a potential response to update user on status of code-base parsing. It sends \gls{http}Status 200 OK, along with what is being parsed, whether it is parsing, done parsing or has failed parsing, how many files have been found and the ratio of files that were parsed or not. Files that are not parsed, might include README.md, \gls{git} files or files with unsupported extensions.  

\subsection{Language parsing in JAVA} \label{subsection:parsingJava}
\input{inc/figures/codesnippets/antlrCPPGrammarExample.tex}

Listing \ref{lst:antlrCppGrammarRuleExample} shows the rule defining the syntax for member declaration. 
It specifies that it can be of 7 forms, where each is separated by a vertical bar or OR gate. The first rule specifies that it might contain an attributespeifierseq rule, followed by what might be a declspecifierseq, in turn followed by what might be a memberdeclaratorlist and ends with the ";" character. 

\input{inc/figures/codesnippets/listenerIfBlockExample.tex}
As the grammar file defines the structure of the program, it was highly desired that as much of the parsing as possible was to be handled by \gls{antlr}. If \gls{antlr} handled the scoping and definitions then one could be very certain that no data structure were skipped or mishandled. Listing \ref{lst:ifBlockExample} shows an example of where checking for variables is done manually, rather then relying on more listeners given by \gls{antlr}. This can create a lot of nested if statements to check what form of the rule or nested rule is being matched. This increased the \Gls{cyclomaticcomplexity} and probability of error while also relying on the development team knowing all the niche aspects of a particular data structure. The same is true when merging the output of rules by defining an interval by using the start point of a rule and the endpoint of another. If there are optional rules within the context, then the output can vary greatly. 

% More talk about rules?

\input{inc/figures/codesnippets/antlrCPPListenerExample.tex}
\input{inc/figures/codesnippets/antlrJavaListenerExample.tex}

Listing \ref{lst:antlrCPPListenerExample} and \ref{lst:antlrJavaListenerExample} shows a trimmed down version of the parsing of function definition in C++ and Java respectively. Parsing of the two languages can differ significantly as the naming convention used in the different \gls{antlr} grammar files differ and C++ also has a more flexible syntax. Java grammar might also use different methods for defining lists than C++. 
Due to the differences in Java and C++, they are handled separately based on the file extension. 

Java is read by the JavaParserFacade and interpreted by JavaExtendedListener, while C++ is handled by CppParserFacade and CppExtendedListener class. Each of the extended listeners extend from their respective \gls{antlr} listener and are meant to contain common functionality for all types of parsers for their language. Currently only the initial parsers exist. The initial parsers creates the initial data used for the main project visualization. 

Both \ref{lst:antlrCPPListenerExample} and \ref{lst:antlrJavaListenerExample} listings show the enter function ending with the \newline enterScope(functionModel) call and the exit functions calling exitScope. The enter function is called when the parser reaches the beginning of its respective rule while the exit is called at the end. With the enterScope being called, all following rules being called would have functionModel in memory and know they are matched within the function rule. The check for whether or not the instance of the model is of the expected type in the exit function, were initially undesirable as with a correct and full implementation of the \gls{antlr} grammar, there would be no possibility for an unexpected model and the check relies on the developers understanding of the data structure.
